How Slow do my Transient Type Checks Go?

### 2019-08-17 paper.tex
Remove marker
Signed-off-by: Stefan Marr <git@stefan-marr.de>

\here
As can be seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmarks, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing lattice graphs. For Permute there is actually a significant performance \emph{increase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight increase in performance, but here this is caused by two type annotations (in red and blue); this effect does not appear to be cumulative, however: the purple dots are about the same height as the red and blue ones, so \emph{either} annotation is sufficient for the full benefit.

>>>>

As can be seen, most of the time the patterns we identified in the typing lattice graphs correspond to outliers in the single type annotation column graphs. For the Snake, Towers and CD benchmarks, there is clearly a pattern where an individual type annotation (highlighted in red) appears to be the cause of the slowest/upper half of the typing configurations. For Permute there is actually a significant performance \emph{increase}, indicated by the lower half of the lattice being highlighted in red. DeltaBlue and Go also show a slight increase in performance, but here this is caused by two type annotations (in red and blue); this effect does not appear to be cumulative, however: the purple dots are about the same height as the red and blue ones, so \emph{either} annotation is sufficient for the full benefit.
